### 2015-07-11 narrative/placement.tex
minor edits on life cycle.

\subsubsection*{Purging}
\label{sec:purging-data}
An important phase of the data lifecycle is the purging of data from the system, 
which presents significant challenges, both from the systems and policy perspectives. 
Deciding what data to purge and when to purge it can be non-trivial, and it is 
essential that this is done with the application in the loop. One approach we will 
explore in this efforts will be extending the notion of system and application utility. 
The former can be used to determine when data object need to purged while the 
latter can help determine the relative importance of data objects to the 
application and identify which data objects can be purged. Developing policies 
for purging is a more challenging problem and will require engaging  the 
user community. However, a key research problem that will be addressed in
 this effort is developing the abstractions that can be used to consistently and 
 unambiguously express these policies as well as the mechanisms that can be 
 used to correctly enforce these policies.

>>>>

\subsubsection*{Purging}
\label{sec:purging-data}
An important phase of the data lifecycle is the purging of data from the system, 
which presents significant challenges, both from the systems and policy perspectives. 
Deciding what data to purge and when to purge it can be non-trivial, and it is 
essential that this is done with the application in the loop. 
%One approach we will 
%explore in this efforts will be extending the notion of system and application utility. 
%The former can be used to determine when data chunks need to purged while the 
%latter can help determine the relative importance of data chunks to the 
%application and identify which data chunks can be purged. 
Developing policies 
for purging is a more challenging problem and will require engaging the 
user community. However, a key research problem that will be addressed in
 this effort is developing the abstractions that can be used to consistently and 
 unambiguously express these policies as well as the mechanisms that can be 
 used to correctly enforce these policies.
